---
output: github_document
always_allow_html: yes
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

<!-- badges: start -->
[![Travis-CI Build Status](https://travis-ci.org/yonicd/ripe.svg?branch=master)](https://travis-ci.org/yonicd/ripe)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/yonicd/ripe?branch=master&svg=true)](https://ci.appveyor.com/project/yonicd/ripe)
[![Covrpage Summary](covrpage-Last_Build_2019_11_20-brightgreen.svg)](http://tinyurl.com/vzcsnsa)
<!-- badges: end -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)

library(ripe)
```

# ripe

The goal of ripe is to create a more flexible way to rerun {magrittr} pipes.

## Installation

```{r,eval=FALSE}
remotes::install_github('yonicd/ripe')
```


## Goal 

We want to write the following in a shorter and more flexible way

```{r}

f <- function(){
  
  stats::runif(20)%>%
    sample(10)%>%
    utils::head(5)
}

replicate(n=3,f(),simplify = FALSE)

```

## This is better!

```{r}
stats::runif(20)%>%
  sample(10)%>%
  utils::head(5)%>%
  ripe(replicate,n=4,simplify=FALSE)
```

## Manipulate Chain Replicates

We can now manipulate the chain or move `ripe` around into different subsets of the chain, creating iterative replication workflows.

```{r}

stats::runif(20)%>%
  #sample(10)%>%
  utils::head(5)%>%
  ripe(replicate,n=4,simplify=FALSE)
  
```

## Convert Chain to Lazy

You can also quickly convert the chain to a lazyeval function

```{r}
f <- stats::runif(20)%>%
  sample(10)%>%
  utils::head(5)%>%
  lazy()

f()
f()
```
